### 2017-12-30 icde/revision/sec-exp.tex

\etitle{Exp-4.1}.
%\stitle{Exp-4.1}.
To evaluate the impacts of the time decaying factor $\sigma$, we varied $\sigma$ from -1.6 to -0.4.
%, while fixed $Y_s$ to default values, $T_i=+\infty$, $dif=1$ and $\lambda=0.5$.
The results of \PairAcc are reported in Figs.~\ref{exp-aan-sigma}, \ref{exp-aminer-sigma} and \ref{exp-mag-sigma}.
%with both sets of ground-truth

@@

\etitle{Exp-4.2}.
%\stitle{Exp-4.2}.
To evaluate the impacts of importance weighting factor $\lambda$, we varied $\lambda$ from 0 to 1.
%while fixed $Y_s$ to default values, $T_i=+\infty$, $dif=1$ and $\sigma=-1.0$.
The results of \PairAcc are reported in Figs.~\ref{exp-aan-lambda}, \ref{exp-aminer-lambda} and \ref{exp-mag-lambda}. Note that parameter $\lambda$ has no impacts on efficiency.
%with both sets of ground-truth

@@

\etitle{Exp-4.3}.
To evaluate the impacts of aggregating parameters $\alpha$ and $\beta$, we varied $\alpha$ and $\beta$ at the granularity of 0.01. Again, parameters $\alpha$ and $\beta$ have few impacts on efficiency. The results are reported in Fig.~\ref{exp-ab}, where the parameters $\alpha$ and $\beta$ are set by default (used earlier) to the corresponding values of $\alpha$-axis and $\beta$-axis of the \PairAcc marked with $\star$, respectively.

@@

Moreover, this enables to verify the effectiveness of importance assembling from different components, whose results are reported in Table~IV, in which letters C, V and A stand for citation, venue and author components, respectively.
The ranking based on all components consistently performs the best, using both \recom and \fcita, which justifies the use of importance assembling for ranking scholarly articles.
%which, using \recom and \fcita, improves the \PairAcc over using components (C, V, A, CV, CA, VA) by (5.77\%, 19.4\%, 16.1\%, 0.09\%, 4.59\%, 6.28\%) and (9.54\%, 23.7\%, 5.90\%, 2.50\%, 0.71\%, 4.79\%) on \aan, (6.94\%, 23.7\%, 14.4\%, 0.21\%, 1.56\%, 7.67\%) and (17.68\%, 12.4\%, 9.61\%, 0.33\%, 1.88\%, 6.34\%) on \aminer, and (6.29\%, 16.38\%, 14.45\%, 0.05\%, 2.43\%, 5.02\%) and (11.43\%, 19.2\%, 11.2\%, 1.44\%, 0.77\%, 9.62\%) on \magdata, respectively.

@@

\etitle{Exp-4.4}.
To evaluate the impacts of our TWPageRank, we compared our \ensemblerank with \drank, an alternative of \ensemblerank by removing the peak time in  Eq.~(\ref{eq-infl-weights}) of  TWPageRank, \ie $w(u,v)=e^{\sigma(T_u-T_v)}$. % with a directly exponentially decayed impact weights without peak times, \ie , .
%The two algorithms produce the same popularity while different prestige.
To better understand the impacts, we varied the importance weighting factor $\lambda$ from 0.1 to 1. Note that the ranking results are the same when $\lambda=0$ due to the same popularity computation. The results are reported in Fig.~\ref{exp-drank}, where the numbers represent the improvement of \PairAcc by \ensemblerank over the one by \drank.

>>>>

\etitle{Exp-5.1}.
%\stitle{Exp-4.1}.
To evaluate the impacts of the time decaying factor $\sigma$, we varied $\sigma$ from -1.6 to -0.4.
%, while fixed $Y_s$ to default values, $T_i=+\infty$, $dif=1$ and $\lambda=0.5$.
The results of \PairAcc are reported in Figs.~\ref{exp-aan-sigma}, \ref{exp-aminer-sigma} and \ref{exp-mag-sigma}.
%with both sets of ground-truth

@@

\etitle{Exp-5.2}.
%\stitle{Exp-4.2}.
To evaluate the impacts of importance weighting factor $\lambda$, we varied $\lambda$ from 0 to 1.
%while fixed $Y_s$ to default values, $T_i=+\infty$, $dif=1$ and $\sigma=-1.0$.
The results of \PairAcc are reported in Figs.~\ref{exp-aan-lambda}, \ref{exp-aminer-lambda} and \ref{exp-mag-lambda}. Note that parameter $\lambda$ has no impacts on efficiency.
%with both sets of ground-truth

@@

\etitle{Exp-5.3}.
To evaluate the impacts of aggregating parameters $\alpha$ and $\beta$, we varied $\alpha$ and $\beta$ at the granularity of 0.01. Again, parameters $\alpha$ and $\beta$ have few impacts on efficiency. The results are reported in Fig.~\ref{exp-ab}, where the parameters $\alpha$ and $\beta$ are set by default (used earlier) to the corresponding values of $\alpha$-axis and $\beta$-axis of the \PairAcc marked with $\star$, respectively.

@@

Moreover, this enables to verify the effectiveness of importance assembling from different components, whose results are reported in Table~V, in which letters C, V and A stand for citation, venue and author components, respectively.
The ranking based on all components consistently performs the best, using both \recom and \fcita, which justifies the use of importance assembling for ranking scholarly articles.
%which, using \recom and \fcita, improves the \PairAcc over using components (C, V, A, CV, CA, VA) by (5.77\%, 19.4\%, 16.1\%, 0.09\%, 4.59\%, 6.28\%) and (9.54\%, 23.7\%, 5.90\%, 2.50\%, 0.71\%, 4.79\%) on \aan, (6.94\%, 23.7\%, 14.4\%, 0.21\%, 1.56\%, 7.67\%) and (17.68\%, 12.4\%, 9.61\%, 0.33\%, 1.88\%, 6.34\%) on \aminer, and (6.29\%, 16.38\%, 14.45\%, 0.05\%, 2.43\%, 5.02\%) and (11.43\%, 19.2\%, 11.2\%, 1.44\%, 0.77\%, 9.62\%) on \magdata, respectively.

@@

\etitle{Exp-5.4}.
To evaluate the impacts of our TWPageRank, we compared our \ensemblerank with \drank, an alternative of \ensemblerank by removing the peak time in  Eq.~(\ref{eq-infl-weights}) of  TWPageRank, \ie $w(u,v)=e^{\sigma(T_u-T_v)}$. % with a directly exponentially decayed impact weights without peak times, \ie , .
%The two algorithms produce the same popularity while different prestige.
To better understand the impacts, we varied the importance weighting factor $\lambda$ from 0.1 to 1. Note that the ranking results are the same when $\lambda=0$ due to the same popularity computation. The results are reported in Fig.~\ref{exp-drank}, where the numbers represent the improvement of \PairAcc by \ensemblerank over the one by \drank.
